Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-10 paper-kelompok/main.tex
updated caption schematic

\begin{abstract}
We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
\end{abstract}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3]{power-schematic.png}}
    \caption{DFD of the power subsystem}
    \label{power-dfd}
    \end{figure}

>>>>

\begin{abstract}
We propose a portable visible spectrophotometer with an ability to integrate with a digital microfluidic (DMF) system.
An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
The device had a dimension of 120 x 131 x 207 mm and a weight of 832 g.
The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
The transmittance RMSE was ±11.22\% with ±9.88 nm wavelength error.
The device had a transmittance repeatability of ±2.58\% and wavelength repeatability of ±0.63 nm.
\end{abstract}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3]{power-schematic.png}}
    \caption{Schematic of the power subsystem}
    \label{power-dfd}
    \end{figure}
